% Abstract for the TUM report document
% Included by MAIN.TEX


\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}	





\vspace*{2cm}
\begin{center}
{\Large \bf Abstract}
\end{center}
\vspace{1cm}

% In today's world where billions of people exchange information online, service providers like Facebook, Twitter, Whatsapp store and process tremendous amount of data. Those service providers need distributed scalable storage systems to store and process big volume of data. Even though data are stored in a distributed storage systems, still the huge size of data are bottleneck for performance optimization. Scanning tens of millions rows and few million columns each time are expensive in terms of execution time and processing power. $Materialized$ $Views$ solve this problem by precomputing expensive queries and storing result in a physical table or disk. One of the bottleneck for this approach is constantly maintaining consistency between base table and view table. We propose a $Incremental$ $View$ $Maintenance$ approach to maintain consistency between base table and view table.


In today's world, billions of people exchange information online. Service providers like Facebook, Twitter, Whatsapp store and process huge chunk of data. These service providers need distributed scalable storage systems to store and process large volume of data. Even though data are stored in a distributed storage systems, still the huge size of data can be a bottleneck regarding performance optimization. Scanning billions of rows and millions of columns each time are expensive regarding execution time and processing power. \emph{Materialized Views} solve this problem by pre-computing expensive queries and storing the result in a physical table or disk. One of the bottlenecks for this approach is constantly maintaining consistency between the base table and the view table. In this thesis, we propose an \emph{Incremental View Maintenance} approach to maintain consistency between the base table and the view table.